Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-07-17 manuscript.tex
minor 4.1 update
minor 4.2 update

\subsection{Faculae} \label{sec:soap.faculae}

To see the impact of a facula on the parameters of different models of the CCF, we simulated the effect of an equatorial facula
%\jessi{Should a footnote be added here to explain that the SOAP 2.0 faculae are not simulated from actual faculae templates?} 
of size 3\% relative to the visible stellar hemisphere. The facula is face-on when the phase equals to 0. 
Note that a 3\% faculae is relatively large for the Sun; at maximum activity, large faculae generally have a size of 1\% \citep[e.g.][]{Borgniet-2015}. 
In Fig.~\ref{fig:faculae}, we compare the barycentric variation of the CCF as measured when fitting a Normal density and using its mean (N mean RV), and when fitting a SN density and taking its mean (SN mean RV) or median (SN median RV). We see that all the different estimates of the CCF barycenter present a signal of similar amplitude, however the signal obtained with SN mean RV is notably different from the two others with a maximum amplitude happening at a different phase.

@@

Next we consider the effects on the CCF model parameters due to the presence of an equatorial spot of size 1\% relative to the visible stellar hemisphere. 
The spot is face-on when the phase equals to 0. 
Note that this is a large spot for the Sun, as large spots are generally on the order of 0.1\% \citep[e.g.][]{Borgniet-2015}. 
In Fig.~\ref{fig:spot}, we show the barycentric variations of the CCF induced by this simulated spot. 
In contrast to the case of the facula, all the different estimates of the CCF barycenter for the spot have the same shape in variation; however, the amplitude for SN mean RV is slightly smaller.

@@

As before, the original RV estimates are corrected using Eq.~\eqref{eq:RV:correction}. 
The results of this correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the coefficients involved in Eq.~\eqref{eq:RV:correction} are summarized in Table~\ref{table:spot.test}. 
As with the facula, the proposed correction is able, in the case of the spot, to capture almost entirely the stellar activity signal when considering the SN or Normal parameters, with $R^2$ values for the linear combination larger than 0.99.

>>>>

\subsection{Facula} \label{sec:soap.faculae}

To see the impact of a facula on the parameters of different models of the CCF, we simulated the effect of an equatorial facula
%\jessi{Should a footnote be added here to explain that the SOAP 2.0 faculae are not simulated from actual faculae templates?} 
of size 3\% relative to the visible stellar hemisphere. The facula is face-on when the phase is 0. 
Note that a 3\% faculae is relatively large for the Sun; at maximum activity, large faculae generally have a size of 1\% \citep[e.g.][]{Borgniet-2015}. 
In Fig.~\ref{fig:faculae}, we compare the barycentric variation of the CCF as measured when fitting a Normal density and using its mean (N mean RV), and when fitting a SN density and taking its mean (SN mean RV) or median (SN median RV). We see that all the different estimates of the CCF barycenter present a signal of similar amplitude, however the signal obtained with SN mean RV is notably different from the two others with a maximum amplitude happening at a different phase.

@@

Next we consider the effects on the CCF model parameters due to the presence of an equatorial spot of size 1\% relative to the visible stellar hemisphere. 
The spot is face-on when the phase is 0. 
Note that this is a large spot for the Sun, as large spots are generally on the order of 0.1\% \citep[e.g.][]{Borgniet-2015}. 
In Fig.~\ref{fig:spot}, we show the barycentric variations of the CCF induced by this simulated spot. 
In contrast to the case of the facula, all the different estimates of the CCF barycenter for the spot have the same shape in variation; however, the amplitude for SN mean RV is slightly smaller.

@@

As before, the original RV estimates are corrected using Eq.~\eqref{eq:RV:correction}. 
The results of this correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the coefficients involved in Eq.~\eqref{eq:RV:correction} are summarized in Table~\ref{table:spot.test}. 
As with the facula, the proposed correction is able to capture almost entirely the spot signal when considering the SN or Normal parameters, with $R^2$ values for the linear combination larger than 0.99.
